Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-08 krs-survey.tex
Added a paragraph on memory mechanisms

This survey focuses on this knowledge representation issue: we aims at first
establishing a as-exhaustive-as-possible typology of representation needs for
robotics in the specific context of service robotics, and then at painting the
current landscape of approaches to the knowledge representation problem in the
research community, in order to summarize the major trends and to identify the
possible shortcomings.

@@

@@

@@

@@

\multirow{5}{0.7cm}[0.2cm]{\turn[1.5cm]{90}{\bf Expr. power}} & Logical formalism & Prolog & DL (OWL) & {\sc CycL} &  & ASP &  & & Horn clauses & TFS & \\
 & OWA/CWA & CWA & OWA & ? & ? & CWA & ? & ? & ? & ? & ? \\
 & Modeling uncertainty & +++ (extension) & & & & & & ++ (stochastic) & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Space Representation & & & & & & & & ++  \\
 & Time representation & & & & & & & + (snapshots) & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & ++ & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory models & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & +++ & & & +  \\
 & Knowledge structure alteration & & ++ & & & ++ & & & & ++ &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & + & & \\
 & Non-monotonic reasoning & & & & & +++ & & &  \\
 & Presupposition accommodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external) & & & ++ & & & + \\
 & Learning & & + & & & & & & & ++ &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & +++ \par (semantic maps) & ++ (external amodal model) & & & & & ++ & ++ \\
 & instantiation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & \ldots with sensori-motor layers & & & & & & & + & + \\
 & \ldots with executive layers & & & & & & & + & ++ \\
 & NLP & & +++ (external) & & & +++ & & +++ & & +++ & \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & + & & +++ (Token test) & & & \\

>>>>

This survey focuses on this knowledge representation issue: we aims at first
establishing a comprehensive typology of representational needs for
robotics in the specific context of service robotics, and then at painting the
current landscape of approaches to the knowledge representation problem in the
research community, in order to summarize the major trends and to identify the
possible shortcomings.

@@

It worth emphasing that if memory is commonly associated to the process of
forgetting facts after a variable amount of \emph{time}, it covers actually
more mechanisms that are relevant to robotics, like selective remembering
triggered by a specific context or reinforcement learning.

@@

\subsubsection{Intrinsic Motivation}

\cite{Oudeyer2007} -> page 2 gives a detailled account of psychological grounds.
Curiosity, Pro-active behaviour...

@@

In~\cite{Hawes2011}, Hawes et al. also explore \emph{curiosity} mechanisms in
the context of spatial representations.

@@

\multirow{5}{0.7cm}[0.2cm]{\turn[1.5cm]{90}{\bf Expr. power}} & Logical formalism & Prolog & DL (OWL) & {\sc CycL} &  & ASP &  & & Horn clauses & TFS & \\
 & OWA/CWA & CWA & OWA & ? & ? & CWA & ? & ? & ? & ? & ? \\
 & Modeling uncertainty & +++ (extension) & & & & & & ++ (stochastic) & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Space Representation & & & & & & & & ++  \\
 & Time representation & & & & & & & + (snapshots) & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & ++ & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory models & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & +++ & & & +  \\
 & Knowledge structure alteration & & ++ & & & ++ & & & & ++ &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & + & & \\
 & Non-monotonic reasoning & & & & & +++ & & &  \\
 & Presupposition accommodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external) & & & ++ & & & + \\
 & Learning & & + & & & & & & & ++ &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & +++ \par (semantic maps) & ++ (external amodal model) & & & & & ++ & ++ \\
 & Intrinsic Motivation & & & & ++ & & & & \\
 & Dynamic instantiation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & \ldots with sensori-motor layers & & & & & & & + & + \\
 & \ldots with executive layers & & & & & & & + & ++ \\
 & NLP & & +++ (external) & & & +++ & & +++ & & +++ & \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & + & & +++ (Token test) & & & \\
